\chapter{COPYRIGHT AND TRADEMARK}
© Copyright 2020. Tzunami Inc. All rights reserved.\\ \\
All intellectual property rights in this publication are owned by Tzunami, Inc. and protected by the United States copyright laws, other applicable copyright laws and international treaty provisions. Tzunami, Inc. retains all rights not expressly granted. No part of this publication may be reproduced in any form whatsoever or used to make any derivative work without prior written approval by Tzunami, Inc.
\\ \\
No representation of warranties for fitness for any purpose other than what is specifically stated in this guide is made either by Tzunami, Inc. or by its agents.
\\ \\
Tzunami, Inc. reserves the right to revise this publication, and/or make improvements or changes in the product(s) and/or the program(s) described in this documentation at any time without prior notice.
\\ \\
Any software on removable media described in this publication is furnished under a license agreement included with the product as a separate document. If you are unable to locate a copy, please contact Tzunami, Inc. and a copy will be forwarded to you.
\\ \\
Tzunami is either a registered trademark or a trademark of Tzunami, Inc. in the United States and/or other countries.
\\\\
All other brands or product names are trademarks or registered trademarks of their respective companies.
\\ \\
For further information, you can contact Tzunami Inc. at: 
\\
Tzunami Inc. \\
601 108th Avenue, NE \\
Suite 1900\\
Bellevue, WA 98004, USA\\
\href{mailto: sales@tzunami.com}{sales@tzunami.com}
\href{mailto: support@tzunami.com}{support@tzunami.com}\\
\url{http://www.tzunami.com}